---
title: "Imputing Missing Data"
author: "Bryan Kim"
date: "11/14/2020"
output: html_document
---

### Regression vs KNN Imputation Methods Results
```{r,message=FALSE,warning=FALSE}
library(ggplot2); library(dplyr); library(tidyr);library(haven);library(readstata13);
library(foreign);library(mice);library(knitr);library(tables)

## "kNN" is the data with imputed FPG values using KNN method (did it in Python and just wrote a new csv file to read into R)
kNN=read.csv("/Users/bryankim/Documents/NBER/Framingham /Data/kNN.csv")
### I do the comparison on one cycle - nhanes 1999-2000
nhanes = read_dta("/Users/bryankim/Documents/NBER/Framingham /Data/nhanes_1999_2000_frs.dta")

## This gets the imputed FPG values using the first regression method (FPG ~ HbA1c)
nhanes= nhanes[complete.cases(nhanes[ , c("lbxgh")]),]; fit = lm(nhanes$fpg ~ nhanes$lbxgh);pred = predict(fit, newdata = ic(nhanes)); nhanes = mutate(nhanes,imputed_fpg = pred) 
## This gets the imputed FPG values using the second regression method (FPG ~ HbA1c + age-sex dummies)
source("/Users/bryankim/Documents/NBER/Framingham /Code/adjust_weight_single_year.R")
fit = lm(nhanes$fpg ~ nhanes$lbxgh + nhanes$M1 + nhanes$M2 + nhanes$M3 + nhanes$M4 + nhanes$F1 + nhanes$F2 + nhanes$F3 + nhanes$F4);pred = predict(fit, newdata = ic(nhanes)); nhanes = mutate(nhanes,imputed_fpg2 = pred)

nhanes = nhanes %>% mutate(reg_fpg1 = ifelse(is.na(fpg),imputed_fpg,fpg)) # First imputed variable is reg_fpg1
nhanes = nhanes %>% mutate(reg_fpg2 = ifelse(is.na(fpg),imputed_fpg2,fpg)) # Second imputed variable is reg_fpg2

## getting our imputed FPG variable using KNN method
nhanes$fpg_knn=kNN$X1
```

### Analyzing scores between complete cases of fpg and HbA1c cases. 
```{r,message=FALSE}
# To start, I am seeing how similar each of the FPG and HbA1c tests for diabetes are.
test=read_dta("/Users/bryankim/Documents/NBER/Framingham /Data/nhanes_1999_2000_frs.dta")
# Keeping only observations where we have BOTH FPG and HbA1c results in NHANES.
test= test[complete.cases(test[ , c("lbxgh","fpg")]),] # Gives us 1098 observations
# Dummy variable positive = 1 if both the FPG test and HbA1c test give us the same result for diabetes (or no diabetes)
test = test %>% mutate(positive = ifelse((fpg >= 126 & lbxgh > 6.5) | (fpg <= 126 & lbxgh < 6.5),1,0))
sum_pos = test %>% select(positive) %>% sum
print(sum_pos)
# So out of the 1098 observations, both tests give the same result for diabetes for 1031 observations (94% similarity)
# Merging with nhanes to use imputed values
test = merge(test,nhanes, all.x=TRUE, on="seqn")
```

### Analyzing the differences between imputation methods (knn and simple linear regression)
```{r,message=FALSE}
## Getting the arithmetic difference between the imputed values of the two methods
nhanes$diff_score = nhanes$imputed_fpg - nhanes$fpg_knn # "imputed_fpg" is the imputed fpg values using linear regression: (fpg ~ HbA1c)
# Absolute value of the mean of this "difference score".
abs(mean(nhanes$diff_score))

## CHECKING CASES
nhanes$cross_val1 = ifelse((nhanes$reg_fpg1 >= 126 & nhanes$lbxgh > 6.5) | (nhanes$reg_fpg1 <= 126 & nhanes$lbxgh < 6.5),1,0)
nhanes$cross_val2 = ifelse((nhanes$reg_fpg2 >= 126 & nhanes$lbxgh > 6.5) | (nhanes$reg_fpg2 <= 126 & nhanes$lbxgh < 6.5),1,0)
nhanes$cross_val3 = ifelse((nhanes$fpg_knn >= 126 & nhanes$lbxgh > 6.5) | (nhanes$fpg_knn <= 126 & nhanes$lbxgh < 6.5),1,0)

nhanes %>% select(cross_val1) %>% sum 
nhanes %>% select(cross_val2) %>% sum
nhanes %>% select(cross_val3) %>% sum

# So there really isn't a huge difference. 
# Using KNN, there are (2225-2134-67) = 24 observations where the imputed value differs from the HbA1c result.

nhanes$simil = ifelse((nhanes$reg_fpg1 >= 126 & nhanes$fpg_knn < 126) | (nhanes$reg_fpg1 <= 126 & nhanes$fpg_knn >= 126),1,0)
nhanes %>% select(simil) %>% sum

```

### INVESTIGATING SOME OF THE DIFFERENCES
```{r}
nhanes_subset = nhanes %>% filter(cross_val1 != cross_val2 | cross_val1 != cross_val3) 
nhanes_subset$HbA1c = nhanes_subset$lbxgh
nhanes_subset = nhanes_subset %>% select(HbA1c,fpg_knn,reg_fpg1,reg_fpg2)
kable(nhanes_subset)

# So it looks like for the HbA1c values really close to the cutoff of 6.5, KNN method and fpg regression differ. 
```

### How many of the discrepancies are inherent differences between the original FPG and HbA1c values? Recall there was a ~94% similarity, so 67 observations where HbA1c marked the individual as diabetic and FPG did not, or vice versa.
```{r,message=FALSE}
nhanes = nhanes %>% mutate(positive = ifelse((fpg >= 126 & lbxgh > 6.5) | (fpg <= 126 & lbxgh < 6.5),1,0))
## Ignoring the NA's, which are there because we have missing FPG or HbA1c values, and filtering for cases where "positive" = 0 (inherent differences): Of this subset, 
nhanes_subset = nhanes %>% filter(positive == 0) 
nhanes_subset = nhanes_subset %>% filter((is.na(fpg))) # there are 7
```
